Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get gender category distribution for each sample
Added pie chart for GLAD/EDGI, NBR and RAMP retro gender

>>>>

```{r Prep gender retro pie chart}

dat.retro_gender_pie <- dat.retro %>% 
  group_by(Sample_plot, Gender_collapsed) %>% 
  summarise(n = n()) %>% 
  mutate(percent = 
           round(n / sum(n) *  100, 1))

```{r Gender retro pie chart by sample}

dat.retro_gender_pie %>% 
  ggplot(aes(x = "", y = percent, fill = Gender_collapsed)) +
  geom_col(stat = "identity") +
  coord_polar("y",start=0) +
  theme_void() +
  scale_fill_manual(values =  COPINGpalette3) +
  facet_wrap(~ Sample_plot, nrow = 1) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.6),
            show.legend = FALSE)
